### 2020-02-02 nlp_models.tex
nlp edits

We have analyzed the four quality metrics described in Section~\ref{sxn:methods} for the OpenAI GPT and GPT2 pretrained models.
See Table \ref{table:nlp} for a summary of results.
We start by examining the PL exponents $\alpha$ for GPT and GPT2 (small).
Observe that all four metrics increase when going from GPT to GPT (small), i.e., they are smaller for the higher-quality model (higher quality since GPT was trained to better data), when the number of layers is held fixed.
Observe also that (with one minor exception involving the Log Frobenius norm metric) all four metrics decrease as one goes from GPT2 medium to GPT2 large to GPT2 xl, indicating that the larger models are indeed better than the smaller models.
%(The one minor exception is the Log Frobenius norm increasing from $1.85$ to $1.86$, for GPT2 large to GPT2 xl.)
\michael{We seem to have typos(s), so I'm not going to flesh out all conclusions I see yet.  The comments I just mad may be wrong, if GPT (small) is really GPT2 (small).  FIX TYPOS AND CLARIFY.}
These results are broadly consistent with the results in Section~\ref{sxn:cv} on series of CV models.

>>>>

We have analyzed the four quality metrics described in Section~\ref{sxn:methods} for the OpenAI GPT and GPT2 pretrained models.
See Table \ref{table:nlp} for a summary of results.
We start by examining the PL exponents $\alpha$ for GPT and GPT2 (small).
Observe that all four metrics increase when going from GPT to GPT (small), i.e., they are smaller for the higher-quality model (higher quality since GPT was trained to better data), when the number of layers is held fixed.
Observe also that (with one minor exception involving the Log Frobenius norm metric) all four metrics decrease as one goes from GPT2 medium to large to xl, indicating that the larger models indeed look better than the smaller models.
%(The one minor exception is the Log Frobenius norm increasing from $1.85$ to $1.86$, for GPT2 large to GPT2 xl.)
\michael{We seem to have typos(s), so I'm not going to flesh out all conclusions I see yet.  The comments I just mad may be wrong, if GPT (small) is really GPT2 (small).  FIX TYPOS AND CLARIFY.}
\charles{GPT2 (small) is GPT--they are the same model}
These results coincide with the results in Section~\ref{sxn:cv} on CV models.
